Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/Introduction.tex
research questions hoofdstuk mooi

@@

The single core execution time in this formula should be measured by used the fastest known single-machine implementation of the algorithm.

>>>>

After determining the most accurate ranking methods, we perform speed-up experiment on distributed MapReduce implementations of those algorithms. We formulate this in the following research question: \\

@@

The single core execution time in this formula is defined as the time that the fastest known single-machine implementation of the algorithm takes to perform the execution.
